Presheaves, Representables and\\the Yoneda Lemma

### 2017-07-03 slides/slides-10/slides-10.tex
Extended slides.

\begin{frame}
  \frametitle{Yoneda Lemma and Yoneda Principle}
  \begin{lemma}[Yoneda]
    Let $\cat A$ be locally small. Then
    \begin{align*}
      [\cat A^\op,\Set](H_A,F)\iso F(A)
    \end{align*}
    naturally in $A\in\cat A$ and $F\in [\cat A^\op,\Set]$.
  \end{lemma}
  \begin{theorem}
    The Yoneda embedding $H_-\from \cat A\to[\cat A^\op,\Set]$ is full and faithful.
  \end{theorem}
  \begin{corollary}[Yoneda Principle]
    Let $\cat A$ be locally small and $A,A'\in\cat A$. Then
    \begin{align*}
      H_A\iso H_{A'} \iff A\iso A'
    \end{align*}
  \end{corollary}
\end{frame}
\end{document}

>>>>

\begin{frame}
  \frametitle{Yoneda Lemma and Yoneda Principle}
  \begin{lemma}[Yoneda]
    Let $\cat A$ be locally small. Then
    \begin{align*}
      [\cat A^\op,\Set](H_A,F)\iso F(A)
    \end{align*}
    naturally in $A\in\cat A$ and $F\in [\cat A^\op,\Set]$.
  \end{lemma}
  \begin{theorem}
    The Yoneda embedding $H_-\from \cat A\to[\cat A^\op,\Set]$ is full and faithful.
  \end{theorem}
  \begin{corollary}[Yoneda Principle]
    Let $\cat A$ be locally small and $A,A'\in\cat A$. Then
    \begin{align*}
      H_A\iso H_{A'} \iff A\iso A'
    \end{align*}
  \end{corollary}
\end{frame}

\begin{frame}
  \frametitle{Cartesian Closedness of Presheaf Category}
  \begin{lemma}
    For any small category $\cat A$, any functor $F\from\cat A^\op\to\Set$ is a colimit of representable functors,
    \begin{align*}
      \lim_{\to I\in\mathbf I} H_{\pi(I)}\iso F
    \end{align*}
    for some small category $\mathbf I$ and functor $\pi\from \mathbf I\to \cat A$.
  \end{lemma}
  \begin{lemma}
    For any $A\in\cat A$, $H_A$ preserves colimits. In particular $$H_A(\lim_{\to\mathbf I} D)\iso \lim_{\to\mathbf I}(H_A\of D)$$ 
    for any small category $\mathbf I$ and functor $D\from\mathbf I\to [\cat A^\op,\Set]$.
  \end{lemma}
\end{frame}

\begin{frame}
  \frametitle{Cartesian Closedness of Presheaf Category (Cont.)}
  \begin{lemma}
    Let $F\from \cat A\to\Set$ be a presheaf. The functor $-\times F\from [\cat A^\op,\Set]\to[\cat A^\op,\Set]$ preserves colomits. That is:
    \begin{align*}
      \lim_{\to \mathbf I} (D\times F)\iso (\lim_{\to \mathbf I} D)\times F
    \end{align*}
    for any small category $\mathbf I$ and functor $D\from\mathbf I\to [\cat A^\op,\Set]$.
  \end{lemma}

  \begin{theorem}
    For any small category $\cat A$, the category of presheaves $\cat A^\op,\Set$ is cartesian closed.
  \end{theorem}
\end{frame}
\end{document}
